---
title: "QSAR Fish Toxicity Data Set](https://archive.ics.uci.edu/ml/datasets/QSAR+fish+toxicity)"
runtime: shiny
output:
  html_document:
    toc: true
  pdf_document:
    toc: false
---

```{r setup, include=FALSE}
library(DT)
library(reshape2)
library(ggplot2)
library(dplyr)
library(plotly)
library(tidyverse)
library(GGally)
library(leaps)
library(scales)
library(corrplot)
knitr::opts_chunk$set(echo = TRUE)
```
## Data
This dataset was used to develop quantitative regression QSAR models to predict acute aquatic toxicity towards the fish Pimephales promelas (fathead minnow) on a set of 908 chemicals. LC50 data, which is the concentration that causes death in 50% of test fish over a test duration of 96 hours, was used as model response. The model comprised 6 molecular descriptors: MLOGP (molecular properties), CIC0 (information indices), GATS1i (2D autocorrelations), NdssC (atom-type counts), NdsCH ((atom-type counts), SM1_Dz(Z) (2D matrix-based descriptors). Details can be found in the quoted reference: M. Cassotti, D. Ballabio, R. Todeschini, V. Consonni. A similarity-based QSAR model for predicting acute toxicity towards the fathead minnow (Pimephales promelas), SAR and QSAR in Environmental Research (2015), 26, 217-243; doi: 10.1080/1062936X.2015.1018938

### Attribute Information
6 molecular descriptors and 1 quantitative experimental response:

1. CIC0
2. SM1_Dz(Z)
3. GATS1i
4. NdsCH
5. NdssC
6. MLOGP
7. quantitative response, LC50 [-LOG(mol/L)]

```{r, echo=FALSE}
dt2 <- read.csv("data/qsar_fish_toxicity.csv", sep = ";", header = FALSE)
# variable names: 
origcnames <- c("CIC0","SM1_Dz(Z)","GATS1i", 
                "NdsCH", "NdssC", "MLOGP", "LC50 [-LOG(mol/L)]")
cnames <- c("CIC0","SM1_Dz","GATS1i", 
            "NdsCH", "NdssC", "MLOGP", "y")
dt2 <- setNames(dt2, cnames)
dt <- dt2
dt <- setNames(dt, cnames)
# data summary table
summarydt <- as.data.frame(do.call(cbind, lapply(dt, summary)))
dtraw <- dt

# normalizing raw data
dtnorm <- data.frame(lapply(dtraw[c("CIC0","SM1_Dz","GATS1i", "MLOGP", "y")], function(x) {
  (x-mean(x))/(max(x) - min(x)) # scaling all variables from 0 to 1
})) 
dtnorm2 <-  cbind(dtnorm[,c("CIC0","SM1_Dz","GATS1i")], 
                  dtraw[,c("NdsCH")], dtraw[,c("NdssC")], dtnorm[,c("MLOGP","y")])
dtnorm2 <- setNames(dtnorm2, cnames)

#dt <- dtnorm2 #using normalized dt in the following analyses
```

### Datatable {.tabset}
#### Raw Data
```{r, echo=FALSE}
DT::datatable(dtraw, class = 'cell-border stripe', rownames = T, extensions = 'Scroller', 
              caption = 'Data', options = list(scrollCollapse = TRUE))
```

#### Normalized Data
```{r, echo=FALSE}
DT::datatable(dt, class = 'cell-border stripe', rownames = T, extensions = 'Scroller', 
              caption = 'Normalized Data ("NdsCH", "NdssC" variables are not normalized)', 
              options = list(scrollCollapse = TRUE))
```

#### Statistics Summary of Normalized Data
```{r, echo=FALSE}
DT::datatable(summarydt, class = 'cell-border stripe', rownames = T, extensions = 'Scroller', 
              caption = 'Data Summary', options = list(scrollCollapse = TRUE))
```

</div>

### Boxplots
```{r, echo=FALSE, eval = T, fig.height=8}
suppressMessages({
  meltdt <- melt(dt)
})
p <- ggplot(data = meltdt, aes(factor(variable),value)) + geom_boxplot() + facet_wrap(~variable, scale="free") + xlab("") + ylab("")
p %>% ggplotly(.) 
```

```{r}
p <- ggplot(data = meltdt, aes(factor(variable),value)) + geom_boxplot() + xlab("") + ylab("")
p %>% ggplotly(.) 
```

### Histograms
#### Histogram of Response Variable
```{r, echo=FALSE}
inputPanel(
  sliderInput("n_breaks", label = "Bandwidth adjustment:",
              min = 5, max = 50, value = 20, step = 1)
)

renderPlot({
  hist(dt$y, probability = F, breaks = as.numeric(input$n_breaks),
       xlab = origcnames[ncol(dt)], main = "Histogram of Response Variable")
})
```

#### Histograms of Explanatory Variables
```{r, echo=FALSE}
inputPanel(
  sliderInput("n_breaks2", label = "Bandwidth adjustment:",
              min = 0.01, max = 1, value = 0.20, step = 0.01)
)

renderPlot({
  ncols = ncol(dt) - 1
  histlist <- lapply(1:ncols, 
                   function(col) ggplot2::qplot(dt[[col]], xlab = origcnames[col],
                                                geom = "histogram", binwidth = input$n_breaks2))
  cowplot::plot_grid(plotlist = histlist)
})
```

### Scatter Plots & Correlations
```{r, echo=FALSE, fig.width= 10, fig.height= 9}
suppressWarnings({
  ggpairs(dt) %>% ggplotly(.) # from GGally package
})
```

### Correlation Heat Map
```{r, echo=FALSE, fig.width=5, fig.height=5}
renderPlot({
  corrplot(cor(dt), method = "number", type = "upper")
})
```

## Models (TODO)
```{r model_helper_fn, echo = F}
getYhat <- function(reg, y) {
  X <- model.matrix(reg)
  bhat <- solve(t(X) %*% X, t(X) %*% y)
  yhat <- X %*% bhat
  return (yhat)
}
getResidualPlot <- function(y, reg) {
  yhat <- getYhat(reg, y)
  resids <- y - yhat
  return (plot(x = yhat, y = resids, xlab = "fitted y", ylab = "residuals"))
}
```

### Using `regsubsets()` to find best-fitted model
```{r}
models <- regsubsets(dt$y ~., data = dt, method = "exhaustive")
models_summary <- summary(models); models_summary
models_res <- data.frame(
  Adj.R2 = which.max(models_summary$adjr2),
  CP = which.min(models_summary$cp)
); models_res # observation: model 6

models_summary$adjr2
```

#### Best-fitted model summary
```{r}
# Using the best model (model 6, selecting all variables) (& generate residual plot):
reg <- lm(dt$y ~ ., data = dt)
summary(reg)
```

#### Residual Plots
```{r, echo = F, fig.height=4, fig.width=4}
# Plot residuals vs. response variable
yhat <- getYhat(reg, dt$y)
resids <- dt$y - yhat
p <- {ggplot(data = dt, aes(x= yhat, y = resids)) + geom_point()} %>% ggplotly(.)
p
```

```{r, echo = F, fig.height=5, fig.width=8}
# Plot residuals vs. all explanatory variables
yhat <- getYhat(reg, dt$y)
resids <- dt$y - yhat
result <- dt[c(-ncol(dt))] # results contain all explanatory variables (excluding y)
result["residuals"] <- resids
dtmelt <- melt(result, "residuals")

p <- {ggplot(data = dtmelt, aes(x= value, y = residuals)) + geom_point() +
    facet_wrap(~variable, scales = "free")} %>% ggplotly(.)
p
```

```{r}

```

