---
title: "[Yacht Hydrodynamics Data Set](https://archive.ics.uci.edu/ml/datasets/Yacht+Hydrodynamics)"
runtime: shiny
output:
  html_document:
    toc: true
  pdf_document:
    toc: false
---

```{r setup, include=FALSE}
library(DT)
library(reshape2)
library(ggplot2)
library(dplyr)
library(plotly)
library(tidyverse)
library(GGally)
library(leaps)
library(scales)
knitr::opts_chunk$set(echo = TRUE)
```
## Data
### Attribute Information
Variations concern hull geometry coefficients and the Froude number:

1. Longitudinal position of the center of buoyancy, adimensional. (**pos**)
2. Prismatic coefficient, adimensional. (**pcoeff**)
3. Length-displacement ratio, adimensional.  (**ld_ratio**)
4. Beam-draught ratio, adimensional. (**bd_ratio**)
5. Length-beam ratio, adimensional.  (**lb_ratio**)
6. Froude number, adimensional.  (**froude**)

The measured variable is the residuary resistance per unit weight of displacement:

7. Residuary resistance per unit weight of displacement, adimensional.

```{r, echo=FALSE}
dt <- read.table("data/yacht_hydrodynamics.data")
origcnames <- c("Longitudinal position of the center of buoyancy",
               "Prismatic coefficient",
               "Length-displacement ratio",
               "Beam-draught ratio",
               "Length-beam ratio",
               "Froude number",
               "Residuary resistance per unit weight of displacement"
               )
cnames <- c("pos","pcoeff","ld_ratio",
                       "bd_ratio", "lb_ratio", "froude","y")
dt <- setNames(dt, cnames)
# data summary table
summarydt <- as.data.frame(do.call(cbind, lapply(dt, summary)))
```

### Datatable {.tabset}
#### Raw Data
```{r, echo=FALSE}
DT::datatable(dt, class = 'cell-border stripe', rownames = T, extensions = 'Scroller', 
              caption = 'Yacht Hydrodynamic Data', options = list(scrollCollapse = TRUE))
```

#### Statistics Summary
```{r, echo=FALSE}
DT::datatable(summarydt, class = 'cell-border stripe', rownames = T, extensions = 'Scroller', 
              caption = 'Data Summary', options = list(scrollCollapse = TRUE))
```

</div>

### Boxplots
```{r, echo=FALSE, eval = T, fig.height=8}
suppressMessages({
  meltdt <- melt(dt)
})
p <- ggplot(data = meltdt, aes(factor(variable),value)) + geom_boxplot() + facet_wrap(~variable, scale="free") + xlab("") + ylab("")
p %>% ggplotly(.) 
```

### Histograms
#### Histogram of Response Variable
```{r, echo=FALSE}
inputPanel(
  sliderInput("n_breaks", label = "Bandwidth adjustment:",
              min = 5, max = 50, value = 20, step = 1)
)

renderPlot({
  hist(log(dt$y), probability = F, breaks = as.numeric(input$n_breaks),
       xlab = origcnames[ncol(dt)], main = "Histogram of Response Variable")
})
```

#### Histograms of Explanatory Variables
```{r, echo=FALSE}
inputPanel(
  sliderInput("n_breaks2", label = "Bandwidth adjustment:",
              min = 0.01, max = 0.5, value = 0.05, step = 0.005)
)

renderPlot({
  ncols = ncol(dt) - 1
  histlist <- lapply(1:ncols, 
                   function(col) ggplot2::qplot(dt[[col]], xlab = origcnames[col],
                                                geom = "histogram", binwidth = input$n_breaks2))
cowplot::plot_grid(plotlist = histlist)
})
```

### Scatter Plots & Correlations
```{r, echo=FALSE, fig.width= 10, fig.height= 9}
suppressWarnings({
  ggpairs(dt) %>% ggplotly(.) # from GGally package
})
```

## Models
TODO
